Coalitions of Uncorrelated Prosumers in a Smart Grid Environment

### 2014-09-12 Article.tex
curve updates

However, these clusters of strongly correlated timeseries are the exact opposite of what we are seeking. We can indeed consider them directly as coalitions and compute their utilities, and the results show, as expected, terrible values (far worse than a random split of the agents in the same number of coalitions).

@@

In more details, figure \ref{fig4:a} presents the evolution of social welfare as the number of coalitions increases (all other parameters are kept constant) for both random (red curve) and clique percolation (blue curve). As for the right plot, it shows the percentage of coalitions able to enter the market for different values of $ P_{\phi}^{MIN} $. For consistency, we average the results of both plots of the random procedure over 100 realizations (5 realizations for clique percolation, but the results are relatively stable), and the errorbars in the plots stands for the standard deviations of the results.

@@

When the grid requirements vary, for very low $ P_{\phi}^{MIN} $, all coalitions for both algorithms are able to enter the market, yielding an acceptance percentage of $ 100 \% $. But as $ P_{\phi}^{MIN} $ increases, we see the percentage of the random procedure quickly dropping while it stays constant for our algorithm. For $ P_{\phi}^{MIN} = 4 $, we see that only a little more than half of the coalitions for the random case are able to enter while all of them enters for the clique percolation algorithm. Finally, when the grid requirement becomes too high, the acceptance percentage of our algorithm tends slowly to zero (only partly shown in this plot for readability).

\begin{figure}
 \centering
  \subcaptionbox{Social Welfare\label{fig4:a}}{\includegraphics[width=1.6in]{figure7/uti}}\hspace{1em}%
  \subcaptionbox{Market entering percentage\label{fig4:b}}{\includegraphics[width=1.6in]{figure4/survival}}
\caption{Evolution of the social welfare \textbf{a)} and the percentage of coalitions able to enter the market \textbf{b)} for different values of $ P_{MIN} $. Blue curves represent clique percolation and the red ones, the random process.}
\label{Fig4}
\end{figure}

>>>>

However, these clusters of strongly correlated timeseries are the exact opposite of what we are seeking. We can indeed consider them directly as coalitions and compute their utilities, and the results show (see the green curves on figure \ref{Fig4}), as expected, terrible values (far worse than a random split of the agents in the same number of coalitions).

@@

In more details, figure \ref{fig4:a} presents the evolution of social welfare as the number of coalitions increases (all other parameters are kept constant) for random (red curve), clique percolation (blue curve), and correlated coalitions (green curves) that stands for a worst case scenario. As for figure \ref{fig4:b}, it shows the percentage of coalitions able to enter the market for different values of $ P_{\phi}^{MIN} $. For consistency, we average the results of both plots of the random procedure over 100 realizations, and the errorbars in the plots stands for the standard deviations of the results.

@@

When the grid requirements vary, for very low $ P_{\phi}^{MIN} $, all coalitions for all algorithms are able to enter the market, yielding an acceptance percentage of $ 100 \% $. But as $ P_{\phi}^{MIN} $ increases, we see the percentage of the correlated coalitions crashing down very quickly. After a few increases in $ P_{\phi}^{MIN} $, the percentage of the random procedure starts droping while it stays almost constant for our algorithm. For $ P_{\phi}^{MIN} = 8 $, we see that only a little more than half of the coalitions for the random case are able to enter while approximately $ 85 \%$ of them enters for the clique percolation algorithm. Finally, when the grid requirement becomes too high, the acceptance percentage of our algorithm tends slowly to zero (not shown in this plot for readability).

\begin{figure}
 \centering
  \subcaptionbox{Social Welfare\label{fig4:a}}{\includegraphics[width=1.6in]{figure7_with_green_curve_v1/uti5}}\hspace{1em}%
  \subcaptionbox{Market entering percentage\label{fig4:b}}{\includegraphics[width=1.6in]{figure4_with_green_curve/survival2_old}}
\caption{Evolution of the social welfare \textbf{a)} and the percentage of coalitions able to enter the market \textbf{b)} for different values of $ P_{MIN} $. Blue curves represent clique percolation, red curves, the random process, and the green ones, correlated coalitions.}
\label{Fig4}
\end{figure}
